A theoretical analysis of the Keep Network random beacon using agent based modeling \\ \thanks{Identify applicable funding agency here. If none, delete this.}

### 2019-09-27 Mesa Simulations/Conference-LaTeX-template_7-9-18 2/paper.tex
steady state active group count

For concentrated distributions such as Ethereum, the steady state level of compromised
groups appears to vary between 0-100 percent (SHOW), with a tendancy to be either close
to 0 or close to 100. For distributions with greater spread, such as our hypothetical linear
distribution, we see steady steat levels within the 60-80 percent band for the given set
of parameters (NOTE PARAMETER SETTINGS). \ref{fig:steady_state}

\subsection{Convergence pressures}
The model primarily converges to steady state due to factors such as
signature request frequency, node availability, group creation/expiration

>>>>

For concentrated distributions such as Ethereum, the steady state level of compromised
groups appears to vary between 0-100 percent (SHOW), with a tendancy to be either close
to 0 or close to 100. For distributions with greater spread, such as our hypothetical linear
distribution, we see steady steat levels within the 60-80 percent band for the given set
of parameters (NOTE PARAMETER SETTINGS) \ref{fig:steady_state}. We expect a similar band but at
different parameter levels for different parameter settings.

\subsection{Convergence pressures}

The model primarily converges to steady state due to factors such as
signature request frequency, node availability, group creation/expiration, and....

\textit{ Steady state active group count:} Groups are generated with every request, and intially
during the bootstrap phase a set number of groups are generated with available nodes. In the current
simulation, requests are generated as coin toss at each step. The steady state number of active groups
is a function of number of new requests and rate of group expiry. Initially we
